Energy and the CES production function

### 2015-11-08 Articles/Article_EcolEcon_2015/EcolEcon_2015A.Rnw
Additional info on corner models.

>>>>

<<Other_Models, eval=FALSE>>=
# These models were estimated and the results sent to Paul Brockway.
# At this point, there is no reason to estimate the modesl every time.

# PT, unadjusted kl, quality-adjusted e
mod_PT_uakl_qae <- cesModel(iGDP ~ iKstkS.L + iL + iUMP + iYear, HistoricalData$PT, nest=c(1,2,3))
summary(mod_PT_uakl_qae)
naturalCoef(mod_PT_uakl_qae)
sum(resid(mod_PT_uakl_qae)^2)

# PT, quality-adjusted kl, unadjusted e
mod_PT_qakl_uae <- cesModel(iGDP ~ iKservS.L + ihLest + iXpMP + iYear, HistoricalData$PT, nest=c(1,2,3))
summary(mod_PT_qakl_uae)
naturalCoef(mod_PT_qakl_uae)
sum(resid(mod_PT_qakl_uae)^2)

# UK, unadjusted kl, quality-adjusted e
mod_UK_uakl_qae <- cesModel(iGDP ~ iKstkO.WwithRD + iL + iU + iYear, HistoricalData$UK, nest=c(1,2,3))
summary(mod_UK_uakl_qae)
naturalCoef(mod_UK_uakl_qae)
sum(resid(mod_UK_uakl_qae)^2)

# UK, quality-adjusted kl, unadjusted e
mod_UK_qakl_uae <- cesModel(iGDP ~ iKservO.WwithRD + ihLest + iXp + iYear, HistoricalData$UK, nest=c(1,2,3))
summary(mod_UK_qakl_uae)
naturalCoef(mod_UK_qakl_uae)
sum(resid(mod_UK_qakl_uae)^2)
